Global case

### 2025-05-09 lipschitz 2025/Lipitschz.tex
update

	Suppose we already know the upper (and lower by symmetry) bound $\gamma_i$ of $y_i$, then
	we can use the following constraints:\begin{align*}
		\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y}_i \geq y_i - a \gamma_i\\
		\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y}_i \leq y_i + (1-a) \gamma_i,
	\end{align*} where $a$ is a binary variable.

	The following plot shows the above constraints:

@@

   Using these constraints, we can sketch the simplified model:
\begin{enumerate}
	\item For each input node, each output node, and each pre-activation and post-activation node in the hidden layers,  set one variable $y_i$. 
	\item Set constraints for input nodes.
	\item Set linear constraints . In this case, since the meaning of $y_i$ is $x_i-x'_i$, this constraints will not use the bias.
	\item Between pre- and post- activation nodes, set the MILP constraint described above.
\end{enumerate}

	The speed of this model is much faster, comparable to the MILP model for local robustness. However, in practice, this model sometimes lose much accuracy.

	\subsection{Another simplified model}

>>>>

	Given  $\gamma_i$ be the upper bound of $y_i$, then constraints for $\hat{y}_i$ are the follows:\begin{align*}
		\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y}_i \geq y_i - a \gamma_i\\
		\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y}_i \leq y_i + (1-a) \gamma_i,
	\end{align*} where $a$ is a binary variable.

	The following plot illustrates the constraints described above.

@@

   Based on above constraints, we can sketch this simplified model:
\begin{enumerate}
	\item For each input node, each output node, and each pre-activation and post-activation node in the hidden layers,  set one variable $y_i$. 
	\item Set constraints for input nodes.
	\item Set linear constraints . In this case, since the meaning of $y_i$ is $x_i-x'_i$, this constraints will not use the bias.
	\item Between pre- and post- activation nodes, set the MILP constraint described above.
\end{enumerate}

	The advantage of this simplified model is that it only contains the number of binary variables as MILP model for local robustness, hence the running speed of this is much faster comparing to the previous one. The cost is a loss of accuracy when the time is infinite.

	However, in practice, with a reasonable timeout, this simplified model can usually obtain a better bound.

	\subsection{Strength of the simplified model}
